### 2019-07-12 report/chapter04.Rnw
Report based on the new data

<<'Data03', echo=FALSE, warning=FALSE>>= 
rm(list = ls())
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
load(file.path(PATH_RESULTS, "meta.bin.RData"))
load(file.path(PATH_RESULTS, "meta.cont.RData"))
load(file.path(PATH_RESULTS, "meta.surv.RData"))
load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))

@@

# data.ext2 <- pb.process2(data)
@

@@

\section{Publication Bias Test Results} \label{sec:publication.bias.tests}
<<echo=FALSE, warning=FALSE>>=
meta.f <- meta.f %>% rowwise() %>% mutate(pval1.egger = onesided.p(stat = stat.egger, side = side, n = k, test.type = "reg"),
                                pval1.thompson = onesided.p(stat = stat.thompson, side = side, n = k, test.type = "reg"),
                                pval1.begg = onesided.p(stat = stat.begg, side = side, n = k, test.type = "rank"),

                                pval1.harbord = onesided.p(stat = stat.harbord, side = side, n = k, test.type = "reg"),
                                pval1.rucker = onesided.p(stat = stat.rucker, side = side, n = k, test.type = "reg"),
                                pval1.peter = onesided.p(stat = stat.peter, side = side, n = k, test.type = "reg"),
                                pval1.schwarzer = onesided.p(stat = stat.schwarzer, side = side, n = k, test.type = "rank"),
                                pval1.d.tes = pval.d.tes)

meta.bin <- meta.f %>% filter(outcome.type == "bin")
meta.cont <- meta.f %>% filter(outcome.type == "cont")
meta.surv <- meta.f %>% filter(outcome.type == "surv")

#Agreement proportions of publication bias tests:

@@

#Survival:
meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
                                                         egger.begg = sum(egger.begg == "agree")/n())
meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))

@@

#Merging:
test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))

         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
         I2 = max(c(0, 1 - (k-1)/Q)),
         i2f = factor(ifelse(I2 == 0, 1, 0)))

meta.bin <- meta.f %>% filter(outcome.type == "bin")
meta.cont <- meta.f %>% filter(outcome.type == "cont")
meta.surv <- meta.f %>% filter(outcome.type == "surv")

@@

dat_text <- data.frame(
  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
  i2f = factor(rep(0, times = 4)))

p.dist.surv <- meta.surv %>% ungroup() %>% 
  select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
  guides(fill=guide_legend(title=expression(paste(I^2, " Heterogeneity")))) + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black")  + 
  scale_fill_discrete(labels = c("> 0", "= 0")) +
  theme(strip.text.x = element_text(size=7)) + 
  ggtitle("Survival Outcomes") 
#--------------------------------------------------------------------------------------------------------------------#

@@

# Tukey Mean difference plots;
#--------------------------------------------------------------------------------------------------------------------#

@@

summary.else <- round(meta.f %>% group_by(test.sum.else) %>% 
                        summarise(n = n()) %>% 
                        select(n)/(dim(meta.cont)[1] + dim(meta.surv)[1]) * 100, 1)

@@

meta.f <- meta.f %>% mutate(egger.test = ifelse(pval1.egger < 0.1/3, 1, 0),
                            thompson.test = ifelse(pval1.thompson < 0.1/3, 1, 0),
                            begg.test = ifelse(pval1.begg < 0.1/3, 1, 0),

@@

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects. Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes. There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer). But note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.surv)[1]}). \\
There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger. Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity. Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset. The obvious correspondence with the heterogeneity statistic however rather suggests that the test is another way to assess between study heterogeneity. Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects. When no heterogeneity is given, Thompson's test results and Egger's test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$). In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\

It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses. A simple method to check the consistency of test results is to compare scatterplots and empirical Spearman correlations between the test statistics. This is done in Figure \ref{fig:test.agreement}. Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results. Also, the $I^2$ statistic is included. Since no test statistic is used for excess significance tests, it is not shown here

@@

#Comparison of log hazard ratios:
sig.d <- meta.f %>% filter(outcome.type == "surv") %>% 
  mutate(d.fixef = est.fixef/se.est.fixef,
         d.ranef = est.ranef/se.est.ranef,
         d.reg = est.reg/se.est.reg,
         d.copas = est.copas/se.est.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
  group_by(method) %>% 
  summarise(significant = length(which(abs(smd) > 1.96)),
            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
sig.d <- data.frame(method = sig.d$method,
                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))

@@

adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.type == "surv") %>% 
  mutate(d.fixef = est.fixef/se.est.fixef,
         d.ranef = est.ranef/se.est.ranef,
         d.reg = est.reg/se.est.reg,
         d.copas = est.copas/se.est.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
  ggplot(aes(x = p.smd)) + 
  geom_histogram(boundary = 0, bins = 20) + 
  theme_bw() + 
  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
#--------------------------------------------------------------------------------------------------------------------#

@@

         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
         I2 = max(c(0, 1 - (k-1)/Q)),
         i2f = factor(ifelse(I2 == 0, 1, 0)),
         se.stat.c = ifelse(outcome.type == "bin", stat.rucker, stat.thompson),
         se.stat = cut(se.stat.c,
                       breaks =  c(-7,1, 2, 4.5)))

meta.bin <- meta.f %>% filter(outcome.type == "bin")
meta.cont <- meta.f %>% filter(outcome.type == "cont")
meta.surv <- meta.f %>% filter(outcome.type == "surv")

@@

#Log hazard ratios:
diff.log.hazard.ratio.fixef <- meta.surv %>% 
  mutate(fixef = est.fixef, ranef = est.ranef,
         copas = est.copas, regression = est.reg) %>% 
  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
                           sign(copas) != sign(fixef) ~ -abs(copas)),
         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
                                sign(regression) != sign(fixef) ~ -abs(regression)),
         fixef = abs(fixef),
         ranef = abs(ranef)) %>% 
  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
  ggplot(aes(x = (fixef - adjusted.log.hazard.ratio))) + 
  geom_histogram(binwidth = 0.1, center = 0) +
  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
#--------------------------------------------------------------------------------------------------------------------#

diff.log.hazard.ratio.ranef <- meta.surv %>% 
  mutate(fixef = est.fixef, ranef = est.ranef,
         copas = est.copas, regression = est.reg) %>% 
  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
                           sign(copas) != sign(ranef) ~ -abs(copas)),
         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
                                sign(regression) != sign(ranef) ~ -abs(regression)),
         fixef = abs(fixef),
         ranef = abs(ranef)) %>% 
  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
  geom_histogram(binwidth = 0.1, center = 0) +
  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
#--------------------------------------------------------------------------------------------------------------------#

@@

adjustmend.diff.surv <- meta.surv %>% 
  transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
                                    sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
            est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
                                    sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),

@@

adjustment.diff.quantile.table <- apply(m.adjustment.diff, 2, 
                                        FUN = function(column){quantile(x = column, 
                                                                        probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
adjustment.diff.mean <- apply(m.adjustment.diff, 2, FUN = function(column) mean(column, na.rm = T))
adjustment.diff.largerzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
adjustment.diff.equalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
adjustment.diff.largerequalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
adjustment.diff.comp.errors <- c(4,4,0,0,0,0,0,0)
adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]), 
                                sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]),
                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]), 
                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]),
                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]), 
                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]),
                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]), 
                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]))
adjustment.diff.missing <- (adjustment.diff.comp.errors + adjustment.diff.noest)/apply(m.adjustment.diff, 2, FUN = function(column) length(column))*100

@@

adjustment.diff.quantile.table.surv <- apply(m.adjustment.diff.surv, 2, 
                                             FUN = function(column){quantile(x = column, 
                                                                             probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
adjustment.diff.largerzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
adjustment.diff.equalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
adjustment.diff.largerequalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
adjustment.diff.comp.errors.surv <- c(0,0,0,0)
adjustment.diff.noest.surv <- c(sum(meta.surv$est.copas.na), sum(meta.surv$est.copas.na),
                                sum(meta.surv$est.reg.na), sum(meta.surv$est.reg.na))
adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100

@@

missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), file.nr = as.character(meta.id),
                                                      comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))

>>>>

<<'Data03', echo=FALSE, warning=FALSE>>= 
rm(list = ls())
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2019-07-04.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results_new')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
load(file.path(PATH_RESULTS, "meta.bin.RData"))
load(file.path(PATH_RESULTS, "meta.cont.RData"))
load(file.path(PATH_RESULTS, "meta.iv.RData"))
load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))

@@

# data.ext2 <- pb.process3(data)
@

@@

\section{Publication Bias Test Results} \label{sec:publication.bias.tests}
<<echo=FALSE, warning=FALSE>>=
#Agreement proportions of publication bias tests:

@@

#IV:
meta.iv <- meta.iv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.surv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
                                                         egger.begg = sum(egger.begg == "agree")/n())
meta.iv <- meta.iv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
agreement.sig.surv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))

@@

#Merging:
test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
#--------------------------------------------------------------------------------------------------------------------#

sig.level <- 0.1
meta.f <- meta.f %>% rowwise() %>% 
  mutate(i2f = factor(ifelse(I2 == 0, 1, 0)))

meta.bin <- meta.f %>% filter(outcome.flag == "DICH")
meta.cont <- meta.f %>% filter(outcome.flag == "CONT")
meta.iv <- meta.f %>% filter(outcome.flag == "IV")

@@

dat_text <- data.frame(
  label = paste(c(sum(meta.iv$begg.test), sum(meta.iv$egger.test), sum(meta.iv$thompson.test), sum(meta.iv$tes.d.test, na.rm = T)), "< 0.1,",
                round(c(mean(meta.iv$begg.test), mean(meta.iv$egger.test), mean(meta.iv$thompson.test), mean(meta.iv$tes.d.test, na.rm = T)),2)*100, "%"),
  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
  i2f = factor(rep(0, times = 4)))

p.dist.surv <- meta.iv %>% ungroup() %>% 
  select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
  guides(fill=guide_legend(title=expression(paste(I^2, " Heterogeneity")))) + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black")  + 
  scale_fill_discrete(labels = c("> 0", "= 0")) +
  theme(strip.text.x = element_text(size=7)) + 
  ggtitle("Survival Outcomes") 
#--------------------------------------------------------------------------------------------------------------------#

@@

# Tukey Mean difference plots;
#--------------------------------------------------------------------------------------------------------------------#
logit <- function(x) log(x/(1-x))

@@

summary.else <- round(meta.f %>% group_by(test.sum.else) %>% 
                        summarise(n = n()) %>% 
                        select(n)/(dim(meta.cont)[1] + dim(meta.iv)[1]) * 100, 1)

@@

meta.f <- meta.f %>% rowwise() %>% mutate(egger.test = ifelse(pval1.egger < 0.1/3, 1, 0),
                            thompson.test = ifelse(pval1.thompson < 0.1/3, 1, 0),
                            begg.test = ifelse(pval1.begg < 0.1/3, 1, 0),

@@

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects. Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes. There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer). But note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.iv)[1]}). \\
There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger. Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity. Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset. The obvious correspondence with the heterogeneity statistic however rather suggests that the test is another way to assess between study heterogeneity. Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects. When no heterogeneity is given, Thompson's test results and Egger's test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$). In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\

\subsection{Publication Bias Test Consistency}
It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses. A simple method to check the consistency of test results is to compare scatterplots and empirical Spearman correlations between the test statistics. This is done in Figure \ref{fig:test.agreement}. Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results. Also, the $I^2$ statistic is included. Since no test statistic is used for excess significance tests, it is not shown here

@@

#Comparison of log hazard ratios:
sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
  mutate(d.fixef = est.fixef/se.est.fixef,
         d.ranef = est.ranef/se.est.ranef,
         d.reg = est.reg/se.est.reg,
         d.copas = est.copas/se.est.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
  group_by(method) %>% 
  summarise(significant = length(which(abs(smd) > 1.96)),
            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
sig.d <- data.frame(method = sig.d$method,
                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))

@@

adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
  mutate(d.fixef = est.fixef/se.est.fixef,
         d.ranef = est.ranef/se.est.ranef,
         d.reg = est.reg/se.est.reg,
         d.copas = est.copas/se.est.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
  ggplot(aes(x = p.smd)) + 
  geom_histogram(boundary = 0, bins = 20) + 
  theme_bw() + 
  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
#--------------------------------------------------------------------------------------------------------------------#

@@

         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
         I2 = max(c(0, 1 - (k-1)/Q)),
         i2f = factor(ifelse(I2 == 0, 1, 0)),
         se.stat.c = ifelse(outcome.flag == "DICH", stat.rucker, stat.thompson),
         se.stat = cut(se.stat.c,
                       breaks =  c(-7,1, 2, 4.5)))

meta.bin <- meta.f %>% filter(outcome.flag == "DICH")
meta.cont <- meta.f %>% filter(outcome.flag == "CONT")
meta.iv <- meta.f %>% filter(outcome.flag == "IV")

@@

#Log hazard ratios:
diff.log.hazard.ratio.fixef <- meta.iv %>% 
  mutate(fixef = est.fixef, ranef = est.ranef,
         copas = est.copas, regression = est.reg) %>% 
  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
                           sign(copas) != sign(fixef) ~ -abs(copas)),
         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
                                sign(regression) != sign(fixef) ~ -abs(regression)),
         fixef = abs(fixef),
         ranef = abs(ranef)) %>% 
  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
  ggplot(aes(x = (fixef - adjusted.log.hazard.ratio))) + 
  geom_histogram(binwidth = 0.1, center = 0) +
  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
#--------------------------------------------------------------------------------------------------------------------#

diff.log.hazard.ratio.ranef <- meta.iv %>% 
  mutate(fixef = est.fixef, ranef = est.ranef,
         copas = est.copas, regression = est.reg) %>% 
  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
                           sign(copas) != sign(ranef) ~ -abs(copas)),
         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
                                sign(regression) != sign(ranef) ~ -abs(regression)),
         fixef = abs(fixef),
         ranef = abs(ranef)) %>% 
  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
  geom_histogram(binwidth = 0.1, center = 0) +
  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
#--------------------------------------------------------------------------------------------------------------------#

@@

adjustmend.diff.surv <- meta.iv %>% 
  transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
                                    sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
            est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
                                    sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),

@@

adjustment.diff.quantile.table <- apply(m.adjustment.diff, 2, 
                                        FUN = function(column){quantile(x = column, 
                                                                        probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
adjustment.diff.mean <- apply(m.adjustment.diff, 2, FUN = function(column) mean(column, na.rm = T))
adjustment.diff.largerzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
adjustment.diff.equalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
adjustment.diff.largerequalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
adjustment.diff.comp.errors <- c(4,4,0,0,0,0,0,0)
adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.flag != "IV"]), 
                                sum(meta.f$est.z.copas.na[meta.f$outcome.flag != "IV"]),
                                sum(meta.f$est.z.reg.na[meta.f$outcome.flag != "IV"]), 
                                sum(meta.f$est.z.reg.na[meta.f$outcome.flag != "IV"]),
                                sum(meta.f$est.d.copas.na[meta.f$outcome.flag != "IV"]), 
                                sum(meta.f$est.d.copas.na[meta.f$outcome.flag != "IV"]),
                                sum(meta.f$est.d.reg.na[meta.f$outcome.flag != "IV"]), 
                                sum(meta.f$est.d.reg.na[meta.f$outcome.flag != "IV"]))
adjustment.diff.missing <- (adjustment.diff.comp.errors + adjustment.diff.noest)/apply(m.adjustment.diff, 2, FUN = function(column) length(column))*100

@@

adjustment.diff.quantile.table.surv <- apply(m.adjustment.diff.surv, 2, 
                                             FUN = function(column){quantile(x = column, 
                                                                             probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
adjustment.diff.largerzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
adjustment.diff.equalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
adjustment.diff.largerequalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
adjustment.diff.comp.errors.surv <- c(0,0,0,0)
adjustment.diff.noest.surv <- c(sum(meta.iv$est.copas.na), sum(meta.iv$est.copas.na),
                                sum(meta.iv$est.reg.na), sum(meta.iv$est.reg.na))
adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100

@@

missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), id = as.character(meta.id),
                                                      comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))
